Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-03 WSSSPE2_report/WSSSPE2_review.tex
Section 4: add email for reference.

>>>>

\begin{comment}  
gvwilson@software-carpentry.org, Colin Venters <C.Venters@hud.ac.uk>,
j.spencer@imperial.ac.uk, erinrobinson@esipfed.org, marpierc@iu.edu,
jwpeterson@gmail.com, abani@buffalo.edu, clenhardt@renci.org, dsk@uchicago.edu,
Samin.Ishtiaq@microsoft.com, james@howison.name, s.a.harris@leeds.ac.uk,
marcus.hanwell@kitware.com, thabermann@hdfgroup.org, rdowns@ciesin.columbia.edu,
cboettig@gmail.com, jakob.blomer@cern.ch, editor@ascl.net 
\end{comment}
